---
title: 'Class11: Scraping Multiple Web Pages'
author: "Olivia Smith"
date: "2026-09-30"
output:
  html_document:
    toc: true
    toc_float: true
    number_selections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Learning obhectives for today 

- scrape multiple webpages using `for` loops; 

- Scrape multiple webpages using the `purrr::map_()` type functions, which would also make you write your own custom functions in R

## Extending the Course Bulletin Scrape for multiple departments

For the sake of this example, let us scrape the following pages: 
[ISA]https://bulletin.miamioh.edu/courses-instruction/isa/ and
[MKT]https://bulletin.miamioh.edu/courses-instruction/mkt/. From the logic shown in class, you can essentially do that for all FSB departments.

Note that if you are doing it just for a few departments, you can just repeat your code a few times; however, this is a bad practice we will not do in this class. Software engineers tend to refer to this as: **DRY** (don't repeat yourself). 
```{r bulletin}
dept_abbr = c('acc', 'bus', 'isa', 'mkt') # extending the example to 4 depts
# line below illustrates how the url can be constructed using pasting0 (i.e, no space) the base url. dpt_abbreviation and the forward slash

##for (counter in 1:length(dept_abbr)) {
  #print(counter)
#}

# OR

courses_df = data.frame() # initialize the container
for (dept_name in dept_abbr) {
  print(dept_name)
  cat( rep("--", 25) )
  print("\n")
  dept_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction/", dept_name, "/")
  
  # for the titles, I will use the selector gadget and for the desc, I will use the inspector (to show you alternative CSS selectors for what we did on Mon)
  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div>p.courseblockdesc") |> 
    rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  df[1,1] |> print() # showing only the first course title
  
  courses_df = rbind(courses_df, df)
  cat(rep("--", 25))
  
}


```

## Re-Examining the Prior Example with the `purrr` package

My preferred approach with the purrr functions is to first create my own function and then use it within the package.

```{r}
scrape_mu_bulletin = function(dept_url){

  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div>p.courseblockdesc") |> 
    rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  
  return(df)
}

test = scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr = c('acc', 'bus', 'isa', 'mkt')
my_urls = paste0(
  "https://bulletin.miamioh.edu/courses-instruction/", # single chr string
  dept_abbr, # vector of four obs
  "/" # single chr string
  )

# the map functions take one or more inputs (depending on the function you are using)
# in this example, we only have 1 input for our function
# so we used map_() instead of map2_() [2 is if you have two inputs], p_map() [for three or more inputs]
# .x = the vector you are itterating over

courses_df_from_purrr = purrr::map_df(.x = my_urls, .f = scrape_mu_bulletin)

head(courses_df_from_purrr)
```















