---
title: "Class10"
author: "Olivia Smith"
date: "2026-09-28"
output: 
  html_document:
    toc: true
    toc_float: true
    number_selections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Robotstxt

The code chunk below will show the output from the [robotstxt package] () for the ISA course bulletin available at:
<https://bulletin.miamioh.edu/courses-instruction/isa/>

```{r}
robotstxt::paths_allowed(paths = "/courses-instruction/isa/", domain = "bulletin.miamioh.edu", bot = "*")
```


## Wikipedia demo
```{r wiki}
robotstxt::paths_allowed(paths = "wiki/", domain = "https://en.wikipedia.org")
```

## LinkedIn demo

from the example below, the `robotstxt` response is inconsistent with what the webpage says and is incorrect. As a general bot, we are not allowed to scrape anything from linkedIn. 

```{r linkedin}
robotstxt::paths_allowed(paths = "jobs/", domain = "https://www.linkedin.com", bot = "*")
```

## Indeed demo
```{r indeed}
robotstxt::paths_allowed(paths = "jobs/", domain = "https://www.indeed.com")
```

** If you removed the slash after the `.com`, the warning disappeared and we got a consistent result with the <https://www.linkedin.com/robots.txt> page


## `rvest` demo: ISA course bulletin

```{r rvest_demo}

isa_page_in_r = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")


#extract the titles
#if all titles look the same on the page, it means they have the same tag/class, which allows you to extract them in one step
#we gpt the selector below by:
## [a] highlighted the course
##[b] right clicked and selected inspect
##[c] found the part that was flushed containing the title
##[d] right clicked and copied the selector
##[e] I saw that the output from the code below just got me the 24th course so I dropped the `:nth-child(24)
isa_page_in_r |>
  rvest::html_elements("#sc_sccoursedescs > div > p.courseblocktitle > strong") |>
  rvest::html_text2() -> isa_titles

# course descriptions
# css selector obtained using the selector gadget
isa_page_in_r |>
  rvest::html_elements(".courseblockdesc") |>
  rvest:: html_text2() -> isa_descs

isa_df = data.frame(
  title = isa_titles, description = isa_descs
)
```



