---
title: "Class 07"
author: "Olivia Smith"
date: "2026-09-16"
output:
  html_document: 
    toc:TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_download: TRUE
    code_folding: show
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Demo
```{r}
con = DBI::dbConnect(RSQLite::SQLite(), "../data/scout.db")
postings = DBI::dbReadTable(con, "scout_postings") |> tibble::as_tibble()
DBI::dbDisconnect(con)

jobs = postings |>
  dplyr::select(company, title, location_state, remote, category, posted_at, last_seen_at) |>
  dplyr::mutate(dplyr::across(dplyr::ends_with("_at"), as.Date),
                days_open = as.numeric(last_seen_at - posted_at))
```

# for Q1 to answer it, we need the following: 
# - number of jobs per category 
# - fracton of those jobs that are remote friendly

jobs |> 
  dplyr::group_by (category)
  dplyr::summarise(
    postings = dplyr::n() #counting the number of rows per category
    remote_share = mean(remote)
    )
    
```
)

# Q2 Among the fulltime jobs, which states have the highest remote share? 
jobs|>
dplyer:: filter(category == 'fulltime')
dplyer::group_by(location_state) |>