---
title: "Class 07"
author: "Olivia Smith"
date: "2026-09-16"
output:
  html_document: 
    toc:TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_download: TRUE
    code_folding: show
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Demo
```{r}
con = DBI::dbConnect(RSQLite::SQLite(), "../data/scout.db")
postings = DBI::dbReadTable(con, "scout_postings") |> tibble::as_tibble()
DBI::dbDisconnect(con)

jobs = postings |>
  dplyr::select(company, title, location_state, remote, category, posted_at, last_seen_at) |>
  dplyr::mutate(dplyr::across(dplyr::ends_with("_at"), as.Date),
                days_open = as.numeric(last_seen_at - posted_at))
```

# for Q1 to answer it, we need the following: 
# - number of jobs per category 
# - fracton of those jobs that are remote friendly

jobs |> 
  dplyr::group_by (category)
  dplyr::summarise(
    postings = dplyr::n() #counting the number of rows per category
    remote_share = mean(remote)
    )
    
```
)

# Q2 Among the fulltime jobs, which states have the highest remote share? 
jobs|>
dplyer:: filter(category == 'fulltime')
dplyer::group_by(location_state) |>

## Practice
```{r}
con = DBI::dbConnect(RSQLite::SQLite(), "../data/midwest_airbnb.db")
listings = DBI::dbReadTable(con, "listings") |>
  tibble::as_tibble()
DBI::dbDisconnect(con)
dplyr::glimpse(listings)

# Q1: Approach (a) would be to simply count the repetitions within the city col
table(listings$city)
# alternatively, group by > summarize (n()) -- that returns a df
# in (a) we returned a named vector

listings |>
  dplyr:: group_by(city)
  dplyr:: summarize(
    city_count = dplyr::n()
    ) --> practice_q1
    
# Q2: 2. For entire homes (room_type == "Entire home/apt") that sleep four or more, what is the median price in each city?
listings |>
  dplyr:: filter(
    room_type == "Entire home/apt" & accomodates >= 4
) |>
  dplyr:: group_by(city) |>
  dplyr: summarize(
  median_price = median(price)
  )
  
  # Q3. 3. Add price_per_person = price / accommodates. Which three listings are cheapest per person? Believe them?
  #Note that this is per listing, and we need to create a new col'
  
  listings |>
  dplyr::mutate
    price_per_person = price / accommodates # LHS = new col name; RHS is the math used to create the new col [this is done row by row]
) |>
  dplyr::arrange(price_per_person) >|
  #you don't need to do this step (next step); I/m just doing it so we can look at output in more compact way (less cols)
    dplyr:: select(city, name, price, accomodates, price_per_person) |>
    head(3) # tail would always proivide bottom 3 (most expensive 3 snce we're sorting in asc order by price_person)
    
    # Which five host_names have the most listings
      dplyr:: count(host_name, sort = T) #short cut for group_by and then n()
```


