---
title: "Hw7"
author: "Olivia Smith"
date: "2026-10-06"
output:
  html_document:
    toc: true
    toc_float: true
    number_selections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## We want to include the following departments in the FSB Directory: 

[ACC](https://miamioh.edu/fsb/directory/?up=/query/all/all/Accountancy/all), 
[ECO](https://miamioh.edu/fsb/directory/?up=/query/all/all/Economics/all), 
[ESP](https://miamioh.edu/fsb/directory/?up=/query/all/all/Entrepreneurship/all),
[FIN](https://miamioh.edu/fsb/directory/?up=/query/all/all/Finance/all),
[ISA](https://miamioh.edu/fsb/directory/?up=/query/all/all/Information%20Systems%20--%20Analytics/all), 
[MKT](https://miamioh.edu/fsb/directory/?up=/query/all/all/Marketing/all),
[MGT](https://miamioh.edu/fsb/directory/?up=/query/all/all/Management/all)

## I tried to make my own code, following the directions as taught in class, failed, then worked with ChatISA to develop a proper answer. First is my attempted code, then is what I worked with on ChatISA to get the right answer. 


dept = c('Accounting','Economics','Entrepreneurship','Finance','Business Analytics','Marketing','Management')

for (abbreviate in dept) {
  cat( rep("-", 50), "\n")
  print(abbreviate)
}
directory_url=paste0(
  'https://miamioh.edu/fsb/directory/?up=/query/all/all/',dept[3], '/', 'all'
  )

webpage = rvest::read_html(directory_url)

webpage |> rvest::html_elements("td") |> rvest::html_text2() -> department

webpage |> rvest::html_elements("#sidebar-main > div > table > tbody > tr > td > i") |> rvest::html_text2() -> descs

df= data.frame(department=department, desc=descs)


```{r}
if(require(rvest)==FALSE) install.packages("rvest")
if(require(httr2)==FALSE) install.packages("httr2")

# Step 1: Check robots.txt to confirm we're allowed to scrape
robots_txt <- httr2::request("https://miamioh.edu/robots.txt") |>
  httr2::req_perform() |>
  httr2::resp_body_string()

cat(robots_txt)

cat("\n\n---------------------------------------\n\n")

# Step 2: Fetch the Accountancy directory page and peek at its structure
accountancy_page <- rvest::read_html("https://miamioh.edu/fsb/directory/?up=/query/all/all/Accountancy/all")

accountancy_page |>
  as.character() |>
  substr(1, 4000) |>
  cat()
```

```{r}
if(require(rvest)==FALSE) install.packages("rvest")

directory_url <- "https://miamioh.edu/fsb/directory/?up=/query/all/all/Accountancy/all"
webpage <- rvest::read_html(directory_url)

# How many tables are on this page?
tables <- webpage |> rvest::html_elements("table")
cat("Number of tables found:", length(tables), "\n\n")

# Look at the raw HTML of just the first table (truncated) so we can see its structure
tables[[1]] |>
  as.character() |>
  substr(1, 3000) |>
  cat()
```

```{r}

if(require(rvest)==FALSE) install.packages("rvest")

main_directory_url <- "https://miamioh.edu/fsb/directory/"
webpage <- rvest::read_html(main_directory_url)

# Find the department dropdown/select options
options <- webpage |> rvest::html_elements("select option")

options |> rvest::html_text2()
options |> rvest::html_attr("value")
```

```{r}
     
if(require(rvest)==FALSE) install.packages("rvest")
if(require(purrr)==FALSE) install.packages("purrr")
if(require(tibble)==FALSE) install.packages("tibble")
if(require(stringr)==FALSE) install.packages("stringr")

# Function to scrape ONE department's directory page
scrape_department <- function(dept_value, dept_label) {

  url <- paste0(
    "https://miamioh.edu/fsb/directory/?up=/query/all/all/",
    dept_value, "/all"
  )

  page <- rvest::read_html(url)
  rows <- page |> rvest::html_elements("table tr")

  rows |>
    purrr::map(function(row) {

      name_node <- row |> rvest::html_element("td strong a")

      # Skip the header row (it has no name link)
      if (is.na(name_node)) return(NULL)

      tibble::tibble(
        department = dept_label,
        name = name_node |>
          rvest::html_text2() |>
          stringr::str_squish(),
        position = row |>
          rvest::html_element("td i") |>
          rvest::html_text2() |>
          stringr::str_squish(),
        website = name_node |> rvest::html_attr("href")
      )
    }) |>
    purrr::list_rbind()
}

# Department labels (for display) and values (for the URL)
depts <- tibble::tibble(
  label = c("Accountancy", "Economics", "Entrepreneurship", "Finance",
            "Information Systems & Analytics", "Marketing", "Management"),
  value = c("Accountancy", "Economics", "Entrepreneurship", "Finance",
            "Information_Systems_and_Analytics", "Marketing", "Management")
)

# Loop the function over all seven departments and combine into one tibble
all_faculty <- purrr::map2(depts$value, depts$label, scrape_department) |>
  purrr::list_rbind()

# Print the first few rows
print(head(all_faculty))
```

```{r}
if(require(dplyr)==FALSE) install.packages("dplyr")

# Count how many rows we got per department
all_faculty |>
  dplyr::count(department)
```